---
title: "STAT 108: Final Project Analysis"
author: "Tim Lanthier"
date: "2/8/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Youtube Analysis
```{r message=FALSE}
library(tidyverse)
library(knitr)
library(patchwork)
library(broom)
library(leaps)
```


```{r}
youtube <- read.csv('data/youtube_data.csv') %>%
  subset(select = -c(X)) # removed redundant X column
glimpse(youtube)
```
We will need to change the types of a few of the variables.
```{r}
youtube <- youtube %>%
  mutate(trending_date = as.Date(trending_date),  # strip time since all trending dates recorded at time 0
         publishedAt = as.POSIXct(publishedAt),
         weekday_published = as.factor(weekday_published))
```

We will now drop some of the columns which we will not use in our analysis. 

```{r}
youtube <- subset(youtube, select = -c(video_id, channelId, categoryId, tags, description, title, channelTitle))
```


## Exploratory Data Analysis

Let's start by checking for missing values. When generating some of the features, we automatically dropped videos which no longer exist anymore. 
```{r}
colSums(is.na(youtube))
```
The only column with missing values is `subscriberCount` and `desc_length`. When using the Youtube API to access subscriber counts, for channels with hidden subscriber counts, we decided to input those values of `subscriberCount` as missing. Seeing as we have so few observations, we will drop these from the dataset. For those with missing description length, this is because those videos have no description. So we will replace those with `desc_length` of 0.

```{r}
youtube$desc_length[is.na(youtube$desc_length)] <- 0
youtube <- youtube %>%
  drop_na()
```


### Univariate

We will start by looking at the distributions for the response variable and each of the predictor variables.

```{r}
ggplot(data = youtube, aes(view_count)) + 
  geom_histogram(bins = 100) +
  labs(x = 'View Count', title = 'Distribution of View Count')

summarise(youtube, mean = mean(view_count), 
          std_dev = sd(view_count),
          min = min(view_count),
          q1 = quantile(view_count, 0.25),
          median = median(view_count),
          q3 = quantile(view_count, 0.75),
          max = max(view_count),
          IQR = q3-q1)
```

Looking at the histogram for view count, we see that the distribution is heavily positively skewed. We also have quite a few outliers. Since we wish to conduct inference, we will be looking at the looking at the log view count.

```{r}
youtube <- youtube %>%
  mutate(log_views = log(view_count))

ggplot(data = youtube, aes(log_views))+
  geom_histogram(bins = 30) +
  labs(x = 'Log View Count', title = 'Distribution of Log View Count')
```
We also will investigate the like to dislike ratio. Note that to avoid division by 0, if we have a video with no dislikes, we will let the like to dislike ratio just be the number of likes.

```{r}
youtube <- youtube %>%
  mutate(like_dislike_ratio = ifelse(dislikes == 0, likes, likes/dislikes)) # avoid division by 0
```


```{r}
p1 <- ggplot(data = youtube, aes(likes))+
  geom_histogram(bins = 30) +
  labs(x = 'Number of Likes', title = 'Distribution of Likes')

p2 <- ggplot(data = youtube, aes(dislikes))+
  geom_histogram(bins = 30) +
  labs(x = 'Number of Dislikes', title = 'Distribution of Dislikes')

p3 <- ggplot(data = youtube, aes(like_dislike_ratio))+
  geom_histogram(bins = 30) +
  labs(x = 'Like to Dislike Ratio', title = 'Distribution of Like to Dislike Ratio')

p4 <- ggplot(data = youtube, aes(comment_count)) +
  geom_histogram(bins = 30) +
  labs(x = 'Comment Count', title = 'Distribution of Comment Count')

p1 + p2 + p3 + p4
```
```{r}
ggplot(data = youtube, aes(desc_length)) +
  geom_histogram(bins = 30) +
  labs(x = 'Length of Description', title = 'Distribution of Description Length')

ggplot(data = youtube, aes(channel_length)) +
  geom_histogram(binwidth = 1)
```


Considering that view count is positively skewed, it is no surprise that the likes, dislikes, and comment count is also positively skewed. Now we will investigate some of the predictors based on the title.

```{r}
p5 <- ggplot(data = youtube, aes(num_caps))+
  geom_histogram(bins = 30)+
  labs(x = 'Number of Capitals Letters in Title')
p6 <- ggplot(data = youtube, aes(num_exc))+
  geom_histogram(bins = 30) +
  labs(x = 'Number of ! in Title')
p7 <- ggplot(data = youtube, aes(num_qm))+
  geom_histogram(bins = 30) +
  labs(x = 'Number of ? in Title')
p8 <- ggplot(data = youtube, aes(num_period))+
  geom_histogram(bins = 30) +
  labs(x = 'Number of Periods in Title')
p9 <- ggplot(data = youtube, aes(num_dollar))+
  geom_histogram(bins = 30) +
  labs(x = 'Number of $ in Title')
p10 <- ggplot(data = youtube, aes(title_length))+
  geom_histogram(bins = 30)+
  labs(x = 'Length of Title')
p5+p6+p7+p8+p9+p10
```



```{r}
p11 <- ggplot(data = youtube, aes(video_length)) +
  geom_histogram(binwidth = 60) +
  labs(x = 'Video Length (Sec)', title = 'Distribution of Video Length')

p12 <- ggplot(data = youtube, aes(num_tags))+
  geom_histogram(binwidth = 10)+
  labs(x = 'Tags', title = 'Distribution of Number of Tags')

p13 <- ggplot(data = youtube, aes(category)) +
  geom_bar() +
  labs(x = 'Category', title = 'Distribution of Category') + 
  theme(axis.text.x = element_text(angle = 90))

p11 + p12 + p13
```
```{r}
p14 <- ggplot(data = youtube, aes(comments_disabled))+
  geom_bar()+
  labs(x = 'Comments Disabled', title = 'Distribution of Comments Disabled')

p15 <- ggplot(data = youtube, aes(ratings_disabled))+
  geom_bar()+
  labs(x = 'Ratings Disabled', title = 'Distribution of Comments Disabled')

p14 + p15
```

```{r}
p16 <- ggplot(data = youtube, aes(trending_date))+
  geom_histogram(binwidth = 14) +
  labs(title = 'Distribution of Trending Date', x = 'Trending Date')

p17<- ggplot(data = youtube, aes(publishedAt))+
  geom_histogram(binwidth = 14*60*60*24)+ # 2 week bin width
  labs(x = 'Date Published', title = 'Distribution of Date Published')

p16 + p17
```
```{r}
levels(youtube$weekday_published) = c('Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday', 'Saturday','Sunday')
```



```{r}
p18 <- ggplot(data = youtube, aes(weekday_published))+
  geom_bar() +
  labs(x = 'Weekday Published', title = 'Distribution of Weekday Published')

p19 <-ggplot(data = youtube, aes(day_published)) +
  geom_histogram(binwidth = 1) +
  labs(x = 'Day Published', title = 'Distribution of Day Published')
  
p20 <- ggplot(data = youtube, aes(hour_published))+
  geom_bar(binwidth = 1) +
  labs(x = 'Hour Published', title = 'Distribution of Hour Published')

p21 <- ggplot(data = youtube, aes(trending_age))+
  geom_bar(binwidth = 1) +
  labs(x = 'TrendingAge', title = 'Distribution of Trending Age')

p18 + p19 + p20 + p21
```
Note that according to Youtube API, time and dates are in UTC time zone.

```{r}
p22 <- ggplot(data = youtube, aes(subscriberCount))+
  geom_histogram(bins = 30) +
  labs(x = 'Subscriber Count', title = 'Distribution of Subscriber Count')
p23 <- ggplot(data = youtube, aes(videoCount)) +
  geom_histogram(bins = 50) +
  labs(x = 'Number of Videos on Channel', title = 'Distribution of Video Count')

p22 + p23

```



### Bivariate

Now we will explore the relationship between our predictor variables and our response variable. As we discussed earlier, we will be using `log_views` instead of `view_count` as our response since we wish to conduct inference. We will start by observing the correlations for some of the numerical data.

```{r}
library(Hmisc)

youtube_num <- youtube %>%
  subset(select = -c(publishedAt, trending_date, comments_disabled, ratings_disabled, weekday_published, category))

cor(youtube_num)
```
Looking at the correlations, we unsurprisingly see some moderate correlation between `log_views` and `likes`, `dislikes`, and `comment_count`. This is unsurprising as naturally videos which have more viewers will have more people rating and commenting on the video. But much like with view count, the likes, dislikes, and comment count on a video will not be observed until after it has been uploading. Since we want to focus on predictor variables that are known at or before the video is uploaded, we will not use these.

Of the variables which are useful in this sense, we see the channel's subscriber count has a moderate postive correlation of 0.484 with `log_views`. We also see that the number of exclamation points has a weak negative correlation as well as the length of the description.

```{r}
b1 <- ggplot(data = youtube, aes(x = likes, y = log_views)) +
  geom_point()

b2 <- ggplot(data = youtube, aes(x = dislikes, y = log_views)) +
  geom_point()

b3 <- ggplot(data = youtube, aes(x = like_dislike_ratio, y = log_views)) +
  geom_point()

b4 <- ggplot(data = youtube, aes(x = comment_count, y = log_views)) +
  geom_point()

b1+b2+b3+b4
```

We might expect a linear relationship between likes/dislikes and the number of views. Since we took the log of views, then if we were to include likes and dislikes in our model, we might want to also take the log of likes and dislikes so we can preserved this relationship. This will likely be true for other variables as well such as subscriber count.

```{r}
b5 <- ggplot(data = youtube, aes(x = comments_disabled, y = log_views)) +
  geom_boxplot()

b6 <- ggplot(data = youtube, aes(x = ratings_disabled, y = log_views)) +
  geom_boxplot()

b5 + b6
```

It looks like disabling ratings might have an effect on `log_views` shown by the different means across videos with disabled and enabled ratings. There is also a small difference in means for videos with comments disabled.

For the sake of plotting some of these variables, we will convert the following variables to factors. 
```{r}
youtube <- youtube %>%
  mutate(num_exc = as.factor(num_exc),
         num_qm = as.factor(num_qm),
         num_period = as.factor(num_period),
         num_dollar = as.factor(num_dollar),
         hour_published = as.factor(hour_published), # convert back after eda
         trending_age = as.factor(trending_age),
         day_published = as.factor(day_published))
```




```{r}
b7 <- ggplot(data = youtube, aes(x = num_tags, y = log_views)) +
  geom_point()

b8 <- ggplot(data = youtube, aes(x = num_caps, y = log_views)) +
  geom_point()

b9 <- ggplot(data = youtube, aes(x = num_exc, y = log_views)) +
  geom_boxplot()

b10 <- ggplot(data = youtube, aes(x = num_qm, y = log_views)) +
  geom_boxplot()

b11 <- ggplot(data = youtube, aes(x = num_period, y = log_views)) +
  geom_boxplot()

b12 <- ggplot(data = youtube, aes(x = num_dollar, y = log_views)) +
  geom_boxplot()

b7+b8+b9+b10+b11+b12
```

Here it looks like the `num_qm` has little to no predictive power. But we do see there is quite a bit of variability for `log_views` across the groups for `num_dollar`, `num_period`, and `num_exc`. Also there might be a weak downward trend for `num_caps` as well. Meanwhile `num_tags` looks completely random. So the number of tags doesn't appear to help us.

```{r}
b13 <- ggplot(data = youtube, aes(x = title_length, y = log_views)) +
  geom_point(alpha = 0.4)

b14 <- ggplot(data = youtube, aes(x = desc_length, y = log_views)) +
  geom_point(alpha = 0.4)

b15 <- ggplot(data = youtube, aes(x = channel_length, y = log_views)) +
  geom_point(alpha = 0.4)

b13+b14+b15
```
Here, the scatterplot for `title_length` looks quite random, as does the scatterplot for `channel_length`. Meanwhile there looks like there might be a weak positive trend for `desc_length`.


```{r}
b15 <- ggplot(data = youtube, aes(x = weekday_published, y = log_views)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90))

b16 <- ggplot(data = youtube, aes(x = day_published, y = log_views)) +
  geom_boxplot()

b17 <- ggplot(data = youtube, aes(x = hour_published, y = log_views)) +
  geom_boxplot()

b18 <- ggplot(data = youtube, aes(x = video_length, y = log_views)) +
  geom_point(alpha = 0.2)

b19 <- ggplot(data = youtube, aes(x = category, y = log_views)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90))

b20 <- ggplot(data = youtube, aes(x = trending_age, y = log_views)) + 
  geom_boxplot()

b15+b16+b17
b18+b19+b20
```

It looks like `trending_age` and `log_views` have an association. This is expected since older videos will have had more time to get more views. That being said, the uploader will not know whether a video will trend or how long it takes to get to trending so it would not make sense to include it in our model. As for the category it looks like `log_views` varies quite a bit between different categories. Hence it might be useful to consider it in our model. For `video_length` it is hard to tell whether there is a relationship. We will construct another plot with adjusted limits

```{r}
ggplot(data = youtube, aes(x = video_length, y = log_views)) +
  geom_point(alpha = 0.3) +
  xlim(0,3000)
```
It is hard to tell whether there is a relationship between `log_views` and `video_length`. If anything, there is a very weak negative relationship between `video_length` and `log_views`, but it is hard to tell due to the difference in variability between short and long videos.



```{r}
b21 <- ggplot(data = youtube, aes(x = subscriberCount, y = log_views)) +
  geom_point()

b22 <- ggplot(data = youtube, aes(x = videoCount, y = log_views)) +
  geom_point()

b21+b22
```

As we noted earlier, it looks like there may be a postive relationship between `subscriberCount` and `log_views`. Meanwhile `videoCount` doesn't seem to be all that useful. Just to check, we will adjust the limits of our plot to get a clearer picture.

```{r}
ggplot(data = youtube, aes(x = videoCount, y = log_views)) +
  geom_point(alpha = 0.3)+
  xlim(0,10000)
```

Based off of this second plot, `videoCount` still does not appear to be all that useful. It doesn't look like the number of video's a channel has affects the number of views a trending video might have. 

```{r}
b23 <- ggplot(data = youtube, aes(x = weekday_published, y =log_views)) +
  geom_boxplot()

b24 <- ggplot(data = youtube, aes(x = hour_published, y =log_views)) +
  geom_boxplot()

b25 <- ggplot(data = youtube, aes(x = day_published, y =log_views)) +
  geom_boxplot()

b24+b23/b25
```

Here it looks like the day of the week in which the video was  doesn't appear to have much of a relationship with `log_views` as the mean of `log_views` is consistent across all days of the week. Meanwhile there is quite a bit of variability in `log_views` across `hour_published`. So `hour_published` might be useful in our model. The same could be said about `day_published` as well.

### Multivariate

Now that we have identified some predictor variables that may be useful, we will explore some of the relationships between them. We will start by looking at `subscriberCount`.


```{r}
m1 <- ggplot(data = youtube, aes(x = category, y = subscriberCount)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90))

m2 <- ggplot(data = youtube, aes(x = comments_disabled, y = subscriberCount)) +
  geom_boxplot()

m3 <- ggplot(data = youtube, aes(x = ratings_disabled, y = subscriberCount)) +
  geom_boxplot()

m4 <- ggplot(data = youtube, aes(x = num_caps, y = subscriberCount)) +
  geom_point(alpha = 0.2)

m5 <- ggplot(data = youtube, aes(x = num_exc, y = subscriberCount)) +
  geom_boxplot()
  
m6 <- ggplot(data = youtube, aes(x = num_period, y = subscriberCount)) +
  geom_boxplot()

m7 <- ggplot(data = youtube, aes(x = num_dollar, y = subscriberCount)) +
  geom_boxplot()

m8 <- ggplot(data = youtube, aes(x = desc_length, y = subscriberCount)) +
  geom_point(alpha = 0.2)

m9 <- ggplot(data = youtube, aes(x = hour_published, y = subscriberCount)) +
  geom_boxplot()

m10 <- ggplot(data = youtube, aes(x = day_published, y = subscriberCount)) +
  geom_boxplot()

m1 + m2
m3 + m4
m5 + m6
m7 +m8
m9 + m10
```

Looking at the above plots, it looks like `category`, `ratings_disabled`, `num_dollar`, `hour_published`, and `day_published` stand out as potentially associated with `subscriberCount` shown by the difference in mean subscriber counts across the groups in each of those predictor variables. For example, the mean subscriber count for videos with ratings disabled is quite a bit higher than the mean subscriber count for the videos with ratings enabled.

```{r}
m11 <- ggplot(data = youtube, aes(fill = comments_disabled, x = category)) +
  geom_bar(position = 'fill') +
  theme(axis.text.x = element_text(angle = 90))

m12 <- ggplot(data = youtube, aes(fill = ratings_disabled, x = category)) +
  geom_bar(position = 'fill') +
  theme(axis.text.x = element_text(angle = 90))

m13 <- ggplot(data = youtube, aes(x = num_caps, y = category)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90))

m14 <- ggplot(data = youtube, aes(fill = num_exc, x = category)) +
  geom_bar(position = 'fill') +
  theme(axis.text.x = element_text(angle = 90))

m15 <- ggplot(data = youtube, aes(fill = num_period, x = category)) +
  geom_bar(position = 'fill') +
  theme(axis.text.x = element_text(angle = 90))

m16 <- ggplot(data = youtube, aes(x = desc_length, y = category)) +
  geom_boxplot()

m17 <- ggplot(data = youtube, aes(fill = hour_published, x = category)) +
  geom_bar(position = 'fill') +
  theme(axis.text.x = element_text(angle = 90))

m18 <- ggplot(data = youtube, aes(fill = day_published, x = category)) +
  geom_bar(position = 'fill') +
  theme(axis.text.x = element_text(angle = 90))

m11+m12
m13+m14
m15+m16
m17+m18
```

Looking at these plots, it looks like the the video category is related to many of the other variables we're interested. The one that doesn't stand out is `ratings_disabled` as the proportion of those with ratings disabled is pretty consistent across categories. Meanwhile for things like the `num_caps` and `desc_length` we see on average a higher number of capital letters and longer length descriptions in Action/Adventure videos.

LIST: subscriberCount, category, comments_disabled, ratings_disabled, num_caps, num_exc, num_period, num_dollar, desc_length, hour_published, day_published

```{r}

```


## Modeling

As discussed earlier, the distribution for `view_count` is heavily skewed. Since the purpose of our analysis is to conduct inference on our model, we would like our response variable to be approximately normally distributed. Hence we will be using `log_views` instead of `view_count` for our predictions. As for the predictor variables, we only want to include predictor variables that the uploader might have knowledge of before uploading. So we will not be using variables such as `likes`, `dislikes`, and `trending_age` since the uploader will not know the values of these variables until the video is uploaded. This narrows down the variables we can use considerably. From our EDA, we noticed the following variables might be useful for predicting the log view count:

`subscriberCount`, `category`, `comments_disabled`, `ratings_disabled`, `num_caps`, `num_exc`, `num_period`, `num_dollar`, `desc_length`, `hour_published`, `day_published`

We can quickly build a model to predict `log_views` with these predictor variables with no interaction terms.

```{r}
test_youtube_data <- youtube %>%
  mutate(num_exc = as.integer(num_exc),
         num_period = as.integer(num_period),
         num_dollar = as.integer(num_dollar),
         hour_published = as.integer(hour_published),
         day_published = as.integer(day_published))
```


```{r}
model1 <- lm(log_views ~ subscriberCount + category + comments_disabled + ratings_disabled + num_caps + num_exc + num_period + num_dollar + desc_length + hour_published + day_published, data = test_youtube_data)

summary(model1)
```




```{r}
full_model <- lm(log_views ~ comments_disabled + ratings_disabled + num_tags + num_caps + num_exc + num_qm + 
                   num_period + num_dollar + title_length + desc_length + weekday_published + day_published + 
                   hour_published + video_length + subscriberCount + videoCount + category + channel_length,
                 data = youtube)

summary(full_model)

test_model <- lm(log_views ~ category, data = youtube)
summary(test_model)
```
```{r}
library(Hmisc)
```
```{r}
res <- cor(youtube)
```
```{r}
library(PerformanceAnalytics)
```


## Checking Assumptions

