---
title: "STAT 108: Final Project Analysis"
author: "Tim Lanthier"
date: "2/8/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Youtube Analysis
```{r message=FALSE}
library(tidyverse)
library(knitr)
library(patchwork)
library(broom)
library(leaps)
```


```{r}
youtube <- read.csv('data/youtube_data.csv') %>%
  subset(select = -c(X)) # removed redundant X column
glimpse(youtube)
```
We will need to change the types of a few of the variables.
```{r}
youtube <- youtube %>%
  mutate(trending_date = as.Date(trending_date),  # strip time since all trending dates recorded at time 0
         publishedAt = as.POSIXct(publishedAt),
         weekday_published = as.factor(weekday_published))
```

We will now drop some of the columns which we will not use in our analysis. 

```{r}
youtube <- subset(youtube, select = -c(video_id, channelId, categoryId, tags, description, title, channelTitle))
```


## Exploratory Data Analysis

Let's start by checking for missing values. When generating some of the features, we automatically dropped videos which no longer exist anymore. 
```{r}
colSums(is.na(youtube))
```
The only column with missing values is `subscriberCount`. When using the Youtube API to access subscriber counts, for channels with hidden subscriber counts, we decided to input those values of `subscriberCount` as missing. Seeing as we have so few observations, we will drop these from the dataset.

```{r}
youtube <- youtube %>%
  drop_na()
```


### Univariate

We will start by looking at the distributions for the response variable and each of the predictor variables.

```{r}
ggplot(data = youtube, aes(view_count)) + 
  geom_histogram(bins = 100) +
  labs(x = 'View Count', title = 'Distribution of View Count')

summarise(youtube, mean = mean(view_count), 
          std_dev = sd(view_count),
          min = min(view_count),
          q1 = quantile(view_count, 0.25),
          median = median(view_count),
          q3 = quantile(view_count, 0.75),
          max = max(view_count),
          IQR = q3-q1)
```

Looking at the histogram for view count, we see that the distribution is heavily positively skewed. We also have quite a few outliers. Since we wish to conduct inference, we will be looking at the looking at the log view count.

```{r}
youtube <- youtube %>%
  mutate(log_views = log(view_count))

ggplot(data = youtube, aes(log_views))+
  geom_histogram(bins = 30) +
  labs(x = 'Log View Count', title = 'Distribution of Log View Count')
```
We also will investigate the like to dislike ratio. Note that to avoid division by 0, if we have a video with no dislikes, we will let the like to dislike ratio just be the number of likes.

```{r}
youtube <- youtube %>%
  mutate(like_dislike_ratio = ifelse(dislikes == 0, likes, likes/dislikes)) # avoid division by 0
```


```{r}
p1 <- ggplot(data = youtube, aes(likes))+
  geom_histogram(bins = 30) +
  labs(x = 'Number of Likes', title = 'Distribution of Likes')

p2 <- ggplot(data = youtube, aes(dislikes))+
  geom_histogram(bins = 30) +
  labs(x = 'Number of Dislikes', title = 'Distribution of Dislikes')

p3 <- ggplot(data = youtube, aes(like_dislike_ratio))+
  geom_histogram(bins = 30) +
  labs(x = 'Like to Dislike Ratio', title = 'Distribution of Like to Dislike Ratio')

p4 <- ggplot(data = youtube, aes(comment_count)) +
  geom_histogram(bins = 30) +
  labs(x = 'Comment Count', title = 'Distribution of Comment Count')

p1 + p2 + p3 + p4
```
```{r}
ggplot(data = youtube, aes(desc_length)) +
  geom_histogram(bins = 30) +
  labs(x = 'Length of Description', title = 'Distribution of Description Length')

ggplot(data = youtube, aes(channel_length)) +
  geom_histogram(binwidth = 1)
```


Considering that view count is positively skewed, it is no surprise that the likes, dislikes, and comment count is also positively skewed. Now we will investigate some of the predictors based on the title.

```{r}
p5 <- ggplot(data = youtube, aes(num_caps))+
  geom_histogram(bins = 30)+
  labs(x = 'Number of Capitals Letters in Title')
p6 <- ggplot(data = youtube, aes(num_exc))+
  geom_histogram(bins = 30) +
  labs(x = 'Number of ! in Title')
p7 <- ggplot(data = youtube, aes(num_qm))+
  geom_histogram(bins = 30) +
  labs(x = 'Number of ? in Title')
p8 <- ggplot(data = youtube, aes(num_period))+
  geom_histogram(bins = 30) +
  labs(x = 'Number of Periods in Title')
p9 <- ggplot(data = youtube, aes(num_dollar))+
  geom_histogram(bins = 30) +
  labs(x = 'Number of $ in Title')
p10 <- ggplot(data = youtube, aes(title_length))+
  geom_histogram(bins = 30)+
  labs(x = 'Length of Title')
p5+p6+p7+p8+p9+p10
```



```{r}
p11 <- ggplot(data = youtube, aes(video_length)) +
  geom_histogram(binwidth = 60) +
  labs(x = 'Video Length (Sec)', title = 'Distribution of Video Length')

p12 <- ggplot(data = youtube, aes(num_tags))+
  geom_histogram(binwidth = 10)+
  labs(x = 'Tags', title = 'Distribution of Number of Tags')

p13 <- ggplot(data = youtube, aes(category)) +
  geom_bar() +
  labs(x = 'Category', title = 'Distribution of Category') + 
  theme(axis.text.x = element_text(angle = 90))

p11 + p12 + p13
```
```{r}
p14 <- ggplot(data = youtube, aes(comments_disabled))+
  geom_bar()+
  labs(x = 'Comments Disabled', title = 'Distribution of Comments Disabled')

p15 <- ggplot(data = youtube, aes(ratings_disabled))+
  geom_bar()+
  labs(x = 'Ratings Disabled', title = 'Distribution of Comments Disabled')

p14 + p15
```

```{r}
p16 <- ggplot(data = youtube, aes(trending_date))+
  geom_histogram(binwidth = 14) +
  labs(title = 'Distribution of Trending Date', x = 'Trending Date')

p17<- ggplot(data = youtube, aes(publishedAt))+
  geom_histogram(binwidth = 14*60*60*24)+ # 2 week bin width
  labs(x = 'Date Published', title = 'Distribution of Date Published')

p16 + p17
```
```{r}
levels(youtube$weekday_published) = c('Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday', 'Saturday','Sunday')
```



```{r}
p18 <- ggplot(data = youtube, aes(weekday_published))+
  geom_bar() +
  labs(x = 'Weekday Published', title = 'Distribution of Weekday Published')

p19 <-ggplot(data = youtube, aes(day_published)) +
  geom_histogram(binwidth = 1) +
  labs(x = 'Day Published', title = 'Distribution of Day Published')
  
p20 <- ggplot(data = youtube, aes(hour_published))+
  geom_bar(binwidth = 1) +
  labs(x = 'Hour Published', title = 'Distribution of Hour Published')

p21 <- ggplot(data = youtube, aes(trending_age))+
  geom_bar(binwidth = 1) +
  labs(x = 'TrendingAge', title = 'Distribution of Trending Age')

p18 + p19 + p20 + p21
```
Note that according to Youtube API, time and dates are in UTC time zone.

```{r}
p22 <- ggplot(data = youtube, aes(subscriberCount))+
  geom_histogram(bins = 30) +
  labs(x = 'Subscriber Count', title = 'Distribution of Subscriber Count')
p23 <- ggplot(data = youtube, aes(videoCount)) +
  geom_histogram(bins = 50) +
  labs(x = 'Number of Videos on Channel', title = 'Distribution of Video Count')

p22 + p23

```



### Bivariate

Now we will explore the relationship between our predictor variables and our response variable. As we discussed earlier, we will be using `log_views` instead of `view_count` as our response since we wish to conduct inference.

```{r}
b1 <- ggplot(data = youtube, aes(x = likes, y = log_views)) +
  geom_point()

b2 <- ggplot(data = youtube, aes(x = dislikes, y = log_views)) +
  geom_point()

b3 <- ggplot(data = youtube, aes(x = like_dislike_ratio, y = log_views)) +
  geom_point()

b4 <- ggplot(data = youtube, aes(x = comment_count, y = log_views)) +
  geom_point()

b1+b2+b3+b4
```

We might expect a linear relationship between likes/dislikes and the number of views. Since we took the log of views, then if we were to include likes and dislikes in our model, we might want to also take the log of likes and dislikes so we can preserved this relationship. This will likely be true for other variables as well such as subscriber count.

```{r}
b5 <- ggplot(data = youtube, aes(x = comments_disabled, y = log_views)) +
  geom_boxplot()

b6 <- ggplot(data = youtube, aes(x = ratings_disabled, y = log_views)) +
  geom_boxplot()

b5 + b6
```

Since we have so few possible values for the following variables, we will convert them to factors.

```{r}
youtube <- youtube %>%
  mutate(num_exc = as.factor(num_exc),
         num_qm = as.factor(num_qm),
         num_period = as.factor(num_period),
         num_dollar = as.factor(num_dollar),
         hour_published = as.factor(hour_published), # convert back after eda
         trending_age = as.factor(trending_age),
         day_published = as.factor(day_published))
```



```{r}
b7 <- ggplot(data = youtube, aes(x = num_tags, y = log_views)) +
  geom_point()

b8 <- ggplot(data = youtube, aes(x = num_caps, y = log_views)) +
  geom_point()

b9 <- ggplot(data = youtube, aes(x = num_exc, y = log_views)) +
  geom_boxplot()

b10 <- ggplot(data = youtube, aes(x = num_qm, y = log_views)) +
  geom_boxplot()

b11 <- ggplot(data = youtube, aes(x = num_period, y = log_views)) +
  geom_boxplot()

b12 <- ggplot(data = youtube, aes(x = num_dollar, y = log_views)) +
  geom_boxplot()

b7+b8+b9+b10+b11+b12
```

```{r}
b13 <- ggplot(data = youtube, aes(x = title_length, y = log_views)) +
  geom_point()

b14 <- ggplot(data = youtube, aes(x = desc_length, y = log_views)) +
  geom_point()

b15 <- ggplot(data = youtube, aes(x = channel_length, y = log_views)) +
  geom_point()

b13+b14+b15
```

```{r}
b15 <- ggplot(data = youtube, aes(x = weekday_published, y = log_views)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90))

b16 <- ggplot(data = youtube, aes(x = day_published, y = log_views)) +
  geom_boxplot()

b17 <- ggplot(data = youtube, aes(x = hour_published, y = log_views)) +
  geom_boxplot()

b18 <- ggplot(data = youtube, aes(x = video_length, y = log_views)) +
  geom_point(alpha = 0.2)

b19 <- ggplot(data = youtube, aes(x = category, y = log_views)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90))

b20 <- ggplot(data = youtube, aes(x = trending_age, y = log_views)) + 
  geom_boxplot()

b15+b16+b17+b18+b19+b20
```

It looks like `trending_age` and `log_views` have an association. This is expected since older videos will have had more time to get more views. 

```{r}
b21 <- ggplot(data = youtube, aes(x = subscriberCount, y = log_views)) +
  geom_point()

b22 <- ggplot(data = youtube, aes(x = videoCount, y = log_views)) +
  geom_point()

b21+b22
```

### Multivariate

Now we will explore some of the interactions between our predictor variables.


```{r}
m1 <- ggplot(data = youtube, aes(x = subscriberCount, y = videoCount, color = log_views)) +
  geom_point()

m2 <- ggplot(data = youtube, aes(x = subscriberCount, y = video_length, color = log_views)) +
  geom_point()

m3 <- ggplot(data = youtube, aes(x = subscriberCount, y = trending_age, color = log_views)) +
  geom_boxplot()

m4 <- ggplot(data = youtube, aes(x = subscriberCount, y = category, color = log_views)) +
  geom_boxplot()

m1 + m2
m3 + m4
  
```

```{r}
m5 <- ggplot(data = youtube, aes(x = subscriberCount, y = desc_length, color = log_views)) +
  geom_point()

m6 <- ggplot(data = youtube, aes(x = subscriberCount, y = title_length, color = log_views)) +
  geom_point()

m7 <- ggplot(data = youtube, aes(x = subscriberCount, y = num_tags, color = log_views)) +
  geom_point()

m5+m6
m7
```

```{r}
m7 <- ggplot(data = youtube, aes(x = title_length, y = desc_length, color = log_views)) +
  geom_point()

m8 <- ggplot(data = youtube, aes(x = title_length, y =, color = log_views)) +
  geom_point()
```


## Transforming our Data

It looks like the log transformation has done a pretty good job of making our data more normally distributed. While not perfect, this might allow us to conduct inference on Log View Count. If we wish to use things likes and dislikes in our model, it would be wise to transform those as well.

## Modeling

As discussed earlier, the distribution for `view_count` is heavily skewed. Since the purpose of our analysis is to conduct inference on our model, we would like our response variable to be approximately normally distributed. Hence we will be using `log_views` instead of `view_count` in our final model. As for the predictor variables, we only want to include predictor variables that the uploader might have knowledge of before uploading. So we will not be using variables such as `likes`, `dislikes`, and `trending_age` since the uploader will not know the values of these variables until the video is uploaded. 

```{r}
test_model <- lm(view_diff ~ category + video_length + num_tags + num_caps + weekday_published + day_published + trending_age + hour_published + video_length + num_exc + num_qm + num_period + num_dollar + subscriberCount, data = youtube)

summary(test_model)
```


## Checking Assumptions

